\documentclass{beamer}
\usetheme{Madrid}
\title{FintechHQ Presentation 3}
\subtitle{Complete end-to-end walkthrough from project motivation to future scope}
\author{Generated Documentation Source}
\date{2026-03-25}
\begin{document}
\begin{frame}
\titlepage
\end{frame}
\begin{frame}{Title Slide}
\begin{itemize}
\item Project: FintechHQ
\item AI-Enabled Financial Intelligence, Analytics, and Paper Trading Platform
\item 2026 presentation edition
\end{itemize}
\end{frame}
\begin{frame}{Project Vision}
\begin{itemize}
\item Build a unified fintech platform for secure access, market research, AI analytics, and paper trading.
\item Reduce fragmentation between charting, fundamentals, news, alerts, learning, and strategy testing.
\item Provide an extensible academic and engineering foundation rather than a single-purpose demo.
\end{itemize}
\end{frame}
\begin{frame}{System Architecture}
\begin{itemize}
\item Next.js 16 frontend with React 19, TypeScript, Tailwind CSS, Radix UI primitives, Recharts, Zustand, Framer Motion, and lightweight-charts for interactive market visualization.
\item FastAPI backend that exposes versioned REST APIs for authentication, user management, stocks, strategies, trading, alerts, community, and education workflows.
\item Dedicated FastAPI ML microservice that handles feature engineering, price prediction, recommendation, risk analytics, fundamental analysis, backtesting, sentiment scoring, and AI chart-pattern detection.
\item PostgreSQL with TimescaleDB-style time-series usage for market and OHLCV storage, supported by Alembic migrations and SQLAlchemy ORM models.
\item Redis for caching, fast state lookups, and service-side infrastructure support.
\item Docker Compose orchestration for frontend, backend, ML service, database, Redis, MLflow, and Flower.
\end{itemize}
\end{frame}
\begin{frame}{Technology Stack}
\begin{itemize}
\item Frontend: Next.js 16 app router, React 19 and TypeScript, Tailwind CSS 4, Radix UI and shadcn-style components, Recharts and lightweight-charts, NextAuth scaffold and local token storage flow, Framer Motion and tsparticles for interactive UI polish
\item Backend: FastAPI, SQLAlchemy 2 async ORM, Alembic migrations, PostgreSQL / TimescaleDB usage pattern, Redis, python-jose for JWT handling, passlib with Argon2, sha256\_crypt, and bcrypt support, slowapi for rate limiting, yfinance, pandas, numpy, ta
\item ML Service: FastAPI ML microservice, PyTorch, scikit-learn, transformers, MLflow, OpenCV headless, Pillow, mplfinance, SciPy and custom algorithmic signal processing
\item DevOps: Docker Compose, Dockerfiles per service, MLflow tracking container, Flower monitoring container, Container networking and mounted development volumes
\end{itemize}
\end{frame}
\begin{frame}{Authentication and Security}
\begin{itemize}
\item Access and refresh JWT tokens with explicit token type claims.
\item Argon2 password hashing with compatibility fallbacks for legacy hash migration.
\item Password policy requiring length, mixed case, numerics, and special characters.
\item Breached-password screening using HaveIBeenPwned k-anonymity API logic.
\item Failed-login tracking and temporary account lockout after repeated failures.
\item User session recording with device fingerprint and IP address capture.
\end{itemize}
\end{frame}
\begin{frame}{Frontend Modules}
\begin{itemize}
\item Auth screens for login, register, password reset, and 2FA setup.
\item Dashboard, portfolio, technical analysis, fundamentals, news, trading, strategies, backtest, risk, alerts, community, and learning routes.
\item Reusable UI widgets including charts, ticker search, password strength meter, order book, and dashboard cards.
\end{itemize}
\end{frame}
\begin{frame}{Backend Modules}
\begin{itemize}
\item Versioned routers for auth, users, stocks, trading, strategies, alerts, social, and education.
\item Service layer for alerts, broker simulation, stock data, education, and social flows.
\item WebSocket layer for price, portfolio, and alert channels.
\end{itemize}
\end{frame}
\begin{frame}{ML and AI Modules}
\begin{itemize}
\item Feature engineering, risk analytics, LSTM forecasting, recommendation engine, and sentiment analysis.
\item Fundamental scoring and DCF-style valuation support.
\item Algorithmic plus CNN-transformer chart-pattern detection with annotation pipeline.
\end{itemize}
\end{frame}
\begin{frame}{Detailed Data Model}
\begin{itemize}
\item User: Identity, account status, risk profile, verification state, lockouts, timestamps, and security relationships.
\item PasswordHistory: Tracks previous password hashes to block reuse.
\item UserSession: Stores per-device session tokens, expiry, fingerprint, and IP metadata.
\item Stock / OHLCVData / FundamentalData: Market master data, historical candles, and stored fundamentals.
\item Portfolio / Position / Transaction: Cash balance, holdings, and transaction ledger for paper trading.
\item Order / Trade: Orders, execution status, fills, and trading activity.
\item Strategy / BacktestRun: User-defined strategies and simulation results.
\item Alert / Notification / AlertHistory: Threshold definitions, user alerts, read-state tracking, and trigger logs.
\item Post / Comment / Like / Follow: Community interaction graph and social feed data.
\item Module / Lesson / UserProgress / Enrollment / Quiz / QuizSubmission: Learning management and progress tracking.
\item Watchlist / WatchlistItem: User-defined monitoring lists.
\item MLPrediction / NewsArticle / NewsSentiment: Predictive outputs and enriched news records.
\end{itemize}
\end{frame}
\begin{frame}{Backend API Catalog}
\begin{itemize}
\item /api/v1/auth/register: Registers a user after uniqueness checks, password policy validation, breach screening, and password-history initialization.
\item /api/v1/auth/login/access-token: Authenticates users, enforces lockouts, supports 2FA branching, and issues access plus refresh tokens.
\item /api/v1/auth/login/verify-2fa: Completes a TOTP-based login challenge and opens a real session.
\item /api/v1/auth/refresh: Refreshes access tokens using refresh-token semantics.
\item /api/v1/auth/2fa/setup: Generates a TOTP secret and provisioning URI.
\item /api/v1/auth/2fa/verify: Finalizes 2FA setup.
\item /api/v1/users/me: Returns the authenticated user profile.
\item /api/v1/users/forgot-password: Generates a reset token with demo-mode response behavior.
\item /api/v1/users/reset-password: Validates reset token, enforces password rules, blocks reuse, and invalidates sessions.
\item /api/v1/stocks/search: Searches stored stocks and supplements results from the curated Indian stock universe.
\item /api/v1/stocks/market-movers: Returns gainers and losers using live or fallback data.
\item /api/v1/stocks/index-stocks: Supplies Nifty, Sensex, or combined symbol catalogs.
\item /api/v1/stocks/\{ticker\}: Returns or hydrates stock master information.
\item /api/v1/stocks/\{ticker\}/ohlcv: Provides candle data from DB or live provider fallback.
\item /api/v1/stocks/\{ticker\}/indicators: Calculates SMA, EMA, RSI, MACD, and Bollinger Bands server-side.
\end{itemize}
\end{frame}
\begin{frame}{Extended Backend API Catalog}
\begin{itemize}
\item /api/v1/stocks/\{ticker\}/quote: Supplies latest quote data.
\item /api/v1/stocks/\{ticker\}/fundamentals: Returns fundamentals and valuation-oriented data.
\item /api/v1/stocks/\{ticker\}/news: Fetches and sentiment-enriches asset-level news.
\item /api/v1/trading/orders: Places or lists paper-trading orders.
\item /api/v1/trading/orders/\{order\_id\}: Cancels pending paper orders.
\item /api/v1/trading/positions: Returns holdings enriched with simulated live prices.
\item /api/v1/trading/portfolio/summary: Provides aggregate portfolio values.
\item /api/v1/alerts: Creates, lists, and deletes alerts.
\item /api/v1/alerts/notifications: Lists and marks notifications as read.
\item /api/v1/strategies: Lists, creates, and deletes strategy definitions.
\item /api/v1/social/feed: Returns social feed content.
\item /api/v1/social/posts: Creates community posts.
\item /api/v1/social/posts/\{id\}/comments: Adds comments to community posts.
\item /api/v1/education/seed: Seeds learning content.
\item /api/v1/education/modules: Lists modules and learning state.
\item /api/v1/education/lessons/\{id\}/complete: Marks lessons complete.
\end{itemize}
\end{frame}
\begin{frame}{ML API Catalog}
\begin{itemize}
\item /api/v1/features/calculate: Generates technical features, candlestick patterns, and support/resistance levels.
\item /api/v1/training/train: Runs model-training related workflows.
\item /api/v1/sentiment/predict: Scores text sentiment for financial context.
\item /api/v1/prediction/train: Trains an LSTM-based price model.
\item /api/v1/prediction/forecast: Forecasts the next price from recent history.
\item /api/v1/recommendation/analyze: Produces a recommendation from price behavior and optional news text.
\item /api/v1/technical/analyze: Runs technical-analysis logic for chart-based insight.
\item /api/v1/risk/analyze: Calculates portfolio risk metrics from holdings and history.
\item /api/v1/fundamental/analyze: Computes DCF and health-score outputs.
\item /api/v1/backtest/run: Executes a simplified backtesting routine.
\item /api/v1/pattern-detection/detect-from-data: Runs ensemble pattern detection and optionally returns annotated charts.
\item /api/v1/pattern-detection/detect-image: Placeholder image-based path pending trained vision weights.
\item /api/v1/pattern-detection/patterns-history: Returns stored detection history.
\item /api/v1/pattern-detection/supported-patterns: Lists supported classical chart patterns.
\end{itemize}
\end{frame}
\begin{frame}{Implementation Honesty}
\begin{itemize}
\item The codebase contains a mix of production-style backend services and UI screens that are either API-integrated or still backed by representative mock data.
\item Authentication, password reset, stock search, quotes, OHLCV retrieval, indicator calculation, alerts, community posting, education seeding, and several ML endpoints are implemented as concrete service flows.
\item Some screens such as portfolio, trade, risk, and backtest currently render realistic demo data in the frontend while the backend and ML layers already expose foundations for fuller integration.
\item The project uses legacy naming in places such as 'FinTech AI Platform' and older repository documents; this document set standardizes the academic/project title as FintechHQ, as requested.
\item Several UI pages still render mock or staged data even though backend service foundations are present.
\item Reset-password flow exposes a reset token in the response for demo convenience and should not do so in production.
\item The 2FA setup page currently uses mocked frontend data rather than invoking the real backend setup endpoint.
\end{itemize}
\end{frame}
\begin{frame}{Academic Takeaways}
\begin{itemize}
\item The project demonstrates domain modeling, full-stack architecture, security engineering, and AI integration in one codebase.
\item It exposes realistic engineering trade-offs between live features and staged UI scaffolds.
\item It is well suited for capstone reporting, professional documentation, and future commercialization paths.
\end{itemize}
\end{frame}
\begin{frame}{User Workflows}
\begin{itemize}
\item User onboarding: A user registers with strong credentials, optionally configures 2FA, receives tokens, and enters the dashboard.
\item Market research: The user searches Indian symbols, loads OHLCV data, studies indicators, checks quotes, reads news, and explores fundamentals.
\item Technical analysis: The technical-analysis screen fetches candles, indicator overlays, quotes, and ML-backed chart-pattern findings.
\item Paper trading: Trading logic validates buying power, updates positions, records transactions, and maintains order state.
\end{itemize}
\end{frame}
\begin{frame}{Current Maturity}
\begin{itemize}
\item The codebase contains a mix of production-style backend services and UI screens that are either API-integrated or still backed by representative mock data.
\item Authentication, password reset, stock search, quotes, OHLCV retrieval, indicator calculation, alerts, community posting, education seeding, and several ML endpoints are implemented as concrete service flows.
\item Some screens such as portfolio, trade, risk, and backtest currently render realistic demo data in the frontend while the backend and ML layers already expose foundations for fuller integration.
\item The project uses legacy naming in places such as 'FinTech AI Platform' and older repository documents; this document set standardizes the academic/project title as FintechHQ, as requested.
\end{itemize}
\end{frame}
\begin{frame}{Limitations and Risks}
\begin{itemize}
\item Several UI pages still render mock or staged data even though backend service foundations are present.
\item Reset-password flow exposes a reset token in the response for demo convenience and should not do so in production.
\item The 2FA setup page currently uses mocked frontend data rather than invoking the real backend setup endpoint.
\item The backend configuration defines an RS256 label, while token creation and decode helpers currently use HS256 symmetric signing internally.
\item Real broker integration is not implemented; trading is a paper-trading simulation.
\item Pattern image detection depends on trained YOLO or related weights and currently documents that limitation in the API response.
\end{itemize}
\end{frame}
\begin{frame}{Future Scope}
\begin{itemize}
\item Live broker integration and fully wired frontend modules.
\item Improved model lifecycle, experiment tracking, and validation.
\item Production-grade secrets, observability, and cloud deployment.
\end{itemize}
\end{frame}
\begin{frame}{Conclusion}
\begin{itemize}
\item FintechHQ already demonstrates strong breadth across fintech, AI, and security engineering.
\item Its modular design supports future growth without major architectural replacement.
\item The project is suitable for academic presentation, viva, and technical review.
\end{itemize}
\end{frame}
\end{document}
