\documentclass{beamer}
\usetheme{Madrid}
\title{FintechHQ Presentation 1}
\subtitle{High-level professional overview of all key project details}
\author{Generated Documentation Source}
\date{2026-03-25}
\begin{document}
\begin{frame}
\titlepage
\end{frame}
\begin{frame}{Title Slide}
\begin{itemize}
\item Project: FintechHQ
\item AI-Enabled Financial Intelligence, Analytics, and Paper Trading Platform
\item 2026 presentation edition
\end{itemize}
\end{frame}
\begin{frame}{Project Vision}
\begin{itemize}
\item Build a unified fintech platform for secure access, market research, AI analytics, and paper trading.
\item Reduce fragmentation between charting, fundamentals, news, alerts, learning, and strategy testing.
\item Provide an extensible academic and engineering foundation rather than a single-purpose demo.
\end{itemize}
\end{frame}
\begin{frame}{System Architecture}
\begin{itemize}
\item Next.js 16 frontend with React 19, TypeScript, Tailwind CSS, Radix UI primitives, Recharts, Zustand, Framer Motion, and lightweight-charts for interactive market visualization.
\item FastAPI backend that exposes versioned REST APIs for authentication, user management, stocks, strategies, trading, alerts, community, and education workflows.
\item Dedicated FastAPI ML microservice that handles feature engineering, price prediction, recommendation, risk analytics, fundamental analysis, backtesting, sentiment scoring, and AI chart-pattern detection.
\item PostgreSQL with TimescaleDB-style time-series usage for market and OHLCV storage, supported by Alembic migrations and SQLAlchemy ORM models.
\item Redis for caching, fast state lookups, and service-side infrastructure support.
\item Docker Compose orchestration for frontend, backend, ML service, database, Redis, MLflow, and Flower.
\end{itemize}
\end{frame}
\begin{frame}{Technology Stack}
\begin{itemize}
\item Frontend: Next.js 16 app router, React 19 and TypeScript, Tailwind CSS 4, Radix UI and shadcn-style components, Recharts and lightweight-charts, NextAuth scaffold and local token storage flow, Framer Motion and tsparticles for interactive UI polish
\item Backend: FastAPI, SQLAlchemy 2 async ORM, Alembic migrations, PostgreSQL / TimescaleDB usage pattern, Redis, python-jose for JWT handling, passlib with Argon2, sha256\_crypt, and bcrypt support, slowapi for rate limiting, yfinance, pandas, numpy, ta
\item ML Service: FastAPI ML microservice, PyTorch, scikit-learn, transformers, MLflow, OpenCV headless, Pillow, mplfinance, SciPy and custom algorithmic signal processing
\item DevOps: Docker Compose, Dockerfiles per service, MLflow tracking container, Flower monitoring container, Container networking and mounted development volumes
\end{itemize}
\end{frame}
\begin{frame}{Authentication and Security}
\begin{itemize}
\item Access and refresh JWT tokens with explicit token type claims.
\item Argon2 password hashing with compatibility fallbacks for legacy hash migration.
\item Password policy requiring length, mixed case, numerics, and special characters.
\item Breached-password screening using HaveIBeenPwned k-anonymity API logic.
\item Failed-login tracking and temporary account lockout after repeated failures.
\item User session recording with device fingerprint and IP address capture.
\end{itemize}
\end{frame}
\begin{frame}{Frontend Modules}
\begin{itemize}
\item Auth screens for login, register, password reset, and 2FA setup.
\item Dashboard, portfolio, technical analysis, fundamentals, news, trading, strategies, backtest, risk, alerts, community, and learning routes.
\item Reusable UI widgets including charts, ticker search, password strength meter, order book, and dashboard cards.
\end{itemize}
\end{frame}
\begin{frame}{Backend Modules}
\begin{itemize}
\item Versioned routers for auth, users, stocks, trading, strategies, alerts, social, and education.
\item Service layer for alerts, broker simulation, stock data, education, and social flows.
\item WebSocket layer for price, portfolio, and alert channels.
\end{itemize}
\end{frame}
\begin{frame}{ML and AI Modules}
\begin{itemize}
\item Feature engineering, risk analytics, LSTM forecasting, recommendation engine, and sentiment analysis.
\item Fundamental scoring and DCF-style valuation support.
\item Algorithmic plus CNN-transformer chart-pattern detection with annotation pipeline.
\end{itemize}
\end{frame}
\begin{frame}{User Workflows}
\begin{itemize}
\item User onboarding: A user registers with strong credentials, optionally configures 2FA, receives tokens, and enters the dashboard.
\item Market research: The user searches Indian symbols, loads OHLCV data, studies indicators, checks quotes, reads news, and explores fundamentals.
\item Technical analysis: The technical-analysis screen fetches candles, indicator overlays, quotes, and ML-backed chart-pattern findings.
\item Paper trading: Trading logic validates buying power, updates positions, records transactions, and maintains order state.
\end{itemize}
\end{frame}
\begin{frame}{Current Maturity}
\begin{itemize}
\item The codebase contains a mix of production-style backend services and UI screens that are either API-integrated or still backed by representative mock data.
\item Authentication, password reset, stock search, quotes, OHLCV retrieval, indicator calculation, alerts, community posting, education seeding, and several ML endpoints are implemented as concrete service flows.
\item Some screens such as portfolio, trade, risk, and backtest currently render realistic demo data in the frontend while the backend and ML layers already expose foundations for fuller integration.
\item The project uses legacy naming in places such as 'FinTech AI Platform' and older repository documents; this document set standardizes the academic/project title as FintechHQ, as requested.
\end{itemize}
\end{frame}
\begin{frame}{Future Scope}
\begin{itemize}
\item Live broker integration and fully wired frontend modules.
\item Improved model lifecycle, experiment tracking, and validation.
\item Production-grade secrets, observability, and cloud deployment.
\end{itemize}
\end{frame}
\begin{frame}{Conclusion}
\begin{itemize}
\item FintechHQ already demonstrates strong breadth across fintech, AI, and security engineering.
\item Its modular design supports future growth without major architectural replacement.
\item The project is suitable for academic presentation, viva, and technical review.
\end{itemize}
\end{frame}
\end{document}
